Various ratios and their estimations

### 2024-07-23 Ratios.Rmd
Just a few changes
Ratio with example

---
title: "Ratios"
output: pdf_document
date: "2024-07-23"
---

@@

  p <- sum(rep((1/1000)*(1/1000), n))
  var_est_boot <- c()
  for (b in 2:B1) {
    # One MC iteration at a time
    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
    random_points$var1 <- mapply(f1, random_points[, 1], random_points[, 2])
    random_points$var2 <- mapply(f2, random_points[, 1], random_points[, 2])
    # a1 <- sum(random_points$var1/p)

    # Bootstrap iterations
    df_boot <- f_boot(random_points, B2)
    # est_boot_val <- mapply(est_boot, df_boot[, 1], df_boot[, 2])
    est_boot_val <- est_boot(df_boot, p)
    est_boot_ratio <- est_boot_val[,1]/est_boot_val[,2]
    var_est_boot <- append(var_est_boot, var(est_boot_ratio))
  }
  return(mean(var_est_boot))
  # Mean of the bootstrap variance
}
```

@@

```{r}
cat("True ratio \"total volume over number of trees\":", sum(trees$v)/nrow(trees), "\nEstimation of this ratio:", est_ratio)
# Ex:
# True ratio "total volume over number of trees": 0.1749312 
# Estimation of this ratio: 0.1693595
```

@@

res_ratio1 <- MC_boot(n, B1 = 1000, B2 = 400, f1 = circle_nb, f2 = circle_vol)
# Just one circle to begin with

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res_ratio1)
# Ex:
# Mean of the variance of bootstrap samples: 
```

@@

```{r}
cat("True ratio \"volume of the smallest over total volume\":", sum(trees[(trees$d130 > 23.5/pi) & (trees$d130 < 70.5/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y1/a2)
```

@@

```{r}
cat("True ratio \"volume of the medium over total volume\":", sum(trees[(trees$d130 > 70.5/pi) & (trees$d130 < 117.5/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y2/a2)
```

@@

```{r}
cat("True ratio \"volume of the biggest over total volume\":", sum(trees[(trees$d130 > 117.5/pi) & (trees$d130 < 500/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y3/a2)
```

```{r}

```

>>>>

---
title: "Various ratios and their estimations"
output: pdf_document
date: "2024-07-23"
---

@@

  p <- sum(rep((1/1000)*(1/1000), n))
  var_est_boot <- c()
  for (b in 2:B1) {
    # One MC iteration at a time
    random_points <- data.frame(x = runif(n, 0, 1000), y = runif(n, 0, 1000))
    random_points$var1 <- mapply(f1, random_points[, 1], random_points[, 2])
    random_points$var2 <- mapply(f2, random_points[, 1], random_points[, 2])

    # Bootstrap iterations
    df_boot <- f_boot(random_points, B2)
    est_boot_val <- est_boot(df_boot, p)
    est_boot_ratio <- est_boot_val[,1]/est_boot_val[,2]
    var_est_boot <- append(var_est_boot, var(est_boot_ratio))
  }
  return(mean(var_est_boot))
  # Mean of the bootstrap variance
}
```

@@

```{r}
cat("True ratio \"total volume over number of trees\":", sum(trees$v)/nrow(trees), "\nEstimation of this ratio:", est_ratio)
# Ex:
# True ratio "total volume over number of trees": 0.1749312 
# Estimation of this ratio: 0.1714633
```

@@

res_ratio1 <- MC_boot(n, B1 = 1000, B2 = 400, f1 = circle_vol, f2 = circle_nb)
# Just one circle to begin with

@@

```{r}
cat("Mean of the variance of bootstrap samples:", res_ratio1)
# Ex:
# Mean of the variance of bootstrap samples: 2190764978
```

@@

```{r}
cat("True ratio \"volume of the smallest over total volume\":", sum(trees[(trees$d130 > 23.5/pi) & (trees$d130 < 70.5/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y1/a2)
# Ex:
# True ratio "volume of the smallest over total volume": 0.5741108
# Estimation of this ratio: 0.5846677
```

res_ratio2 <- MC_boot(n, B1 = 1000, B2 = 400, f1 = circle_vol_size, f2 = circle_vol)
# Just one circle to begin with

```{r}
cat("Mean of the variance of bootstrap samples:", res_ratio2)
```

@@

```{r}
cat("True ratio \"volume of the medium over total volume\":", sum(trees[(trees$d130 > 70.5/pi) & (trees$d130 < 117.5/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y2/a2)
# Ex:
# True ratio "volume of the medium over total volume": 0.3628267
# Estimation of this ratio: 0.3623958
```

@@

```{r}
cat("True ratio \"volume of the biggest over total volume\":", sum(trees[(trees$d130 > 117.5/pi) & (trees$d130 < 500/pi),]$v)/sum(trees$v), "\nEstimation of this ratio:", Y3/a2)
# True ratio "volume of the biggest over total volume": 0.06306254
# Estimation of this ratio: 0.0529365
```
